\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}

### 2020-04-04 docs/paper/paper.tex
WGAN graph

@@

\begin{figure}
	\centering
	\begin{tikzpicture}

	\end{tikzpicture}
	\caption{WGAN architecture}
	\label{fig:gan}
\end{figure}

>>>>

\tikzstyle{metric} = [
	diamond, 
	minimum width=1.2cm, 
	minimum height=1.2cm,
	text centered, 
	draw=black,
	line width=0.3mm,
]

@@

\begin{figure}
	\centering
	\begin{tikzpicture}[node distance=2cm]
		\node(latent) 	[filter,text width=1.4cm] 		{\baselineskip=10pt Noise generator\par};
		\node(generator)[operation,below of=latent] 	{Generator};
		\node(generated)[data, below of=generator,
						 text width=1.4cm]				{\baselineskip=10pt Generated samples\par};
		\node(collected)[data, right of=generated,
						 xshift=1cm,text width=1.4cm]	{\baselineskip=10pt Collected samples\par};
		\node(critic)	[operation,below of=generated,
						 xshift=1.5cm]					{Critic};
		\node(metric)   [metric,below of=critic,
						 text width=1.4cm, yshift=-.2cm]{\baselineskip=10pt{}Wasserstein distance\par};

		\draw [training] (latent) -- (generator) node [pos=.5, right, xshift=0.1cm] (z) {Latent variable};
		\draw [training] (generator) -- (generated);
		\draw [training] (generated) -| (critic);
		\draw [training] (collected) -| (critic);
		\draw [training] (critic) -- (metric);
		\draw [testing]  (metric.east) - ++(1,0) |-  (critic.east);
		\draw [testing]  (metric.west) - ++(-2.2,0) |-  (generator.west);
	\end{tikzpicture}
	\caption{WGAN training}
	\label{fig:gan}
\end{figure}
